Dynamic Topic Modeling for Voice Dialogues

### 2024-05-21 paper/main.tex
update topic evolution and paper

Topic evolution over time on one dialogue:

Topic evolution over time on dataset:

>>>>

\begin{center}
    \centering
    Topic evolution over time on one dialogue:
\end{center}

\begin{lstlisting}
    dialogue_topics_analyze(dialogue, 
                            n_topic_words)
                        \end{lstlisting}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{img/output.png}
    \caption{Topic evolution over time on one dialogue}
\end{figure}

The picture shows the change of themes over time. 
There were 5 segments in this dialog, so 5 timestamps. \\

\begin{center}
    \centering
    Topic evolution over time on dataset:
\end{center}

\begin{lstlisting}
    corpus_topics_analyze(dataset, n_topic_words,
                          top_popular=8, time_range=50)
\end{lstlisting}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.7]{img/ami_topics_evol.png}
    \caption{Topic evolution in AMI dataset}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.7]{img/topic_evol_icsi.png}
    \caption{Topic evolution in ICSI dataset}
\end{figure}

In analyzing the evolution of topics on the dataset, top\_popular is also selected, because there are many more topics on one dialog and it is impossible to analyze everything at once. 
In addition, the time\_range parameter is responsible for reducing time intervals for more convenient analysis.
